\documentclass[a4paper]{article}
\title{}
\author{Jason T. Barkeloo}
\date{\today}
\usepackage[style=numeric-comp,backend=biber,sorting=none]{biblatex}
\usepackage{indentfirst}
\usepackage{lineno, lipsum}
\setlength{\topmargin}{-10mm}
\setlength{\textwidth}{7in}
\setlength{\oddsidemargin}{-8mm}
\setlength{\textheight}{9in}
\setlength{\footskip}{1in}
\hyphenpenalty = 10000
\exhyphenpenalty = 10000
\addbibresource{rs.bib}
\begin{document}

\fontsize{12}{15}
\selectfont
\maketitle


\textbf{Dear UDRI Hiring Manager}\newline\newline
\newline\newline
During my time as a graduate student at the University of Oregon, I was given the opportunity to work at CERN, the European Center of Nuclear Research. Working at CERN was an amazing experience, to be able to work on such a large project with people from all around the world will be an experience I will value for the rest of my life.\newline\newline
While working as a Physicist at CERN, I was responsible for analyzing large amounts of data as part of a team of experts. This taught me the value of collaboration to accomplish complex tasks in a timely manner. Additionally, my work showed my the value of cleaning datasets to give a clearer picture of the system and to reduce processing time.\newline\newline
My experience working on large scale data projects gave me the scientific knowledge necessary to be an essential Data Scientist. Coupled with my extensive coding experience I independently adapted my dissertation research to include machine learning applications.  Developing an end-to-end neural network for signal-background classification allowed me to intimately learn the minutiae involved.  I believe am the ideal candidate for this position.\newline\newline

Thank you,
\newline
\textbf{Jason Barkeloo}

\end{document}
