\cvsection{Experience}

\begin{cventries}

  \cventry
    {Insurance Service Professional II, Personal Lines} % Job title
    {Nationwide Mutual Insurance Company} % Organization
    {Columbus, OH} % Location
    {November 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Assisted members and agents with billing and policy inquiries while maintaining 100\% call quality by adhering to Nationwide's mission and protocols.}
        \item{Applied problem solving skills and leveraged resources to fully resolve issues and identify solutions as the first point of contact.}
        \item{Contributed as a member of the Root Cause Problem Solving (RCPS) team to improve the efficiency and accuracy of call documentation categories.}
        \item{Introduced newly hired associates to the role of ISP and the enterprise's policies and procedures through the shadowing process.}
         	\end{cvitems}
    } 

  \cventry
    {Research Analyst} % Job title
    {Pentagon Federal Credit Union} % Organization
    {Eugene, OR} % Location
    {November 2017 - October 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Responded to a high volume of member inquiries via email and other channels, prepared and proofread formal letters, provided technical support and troubleshooting for the webiste and mobile application.}
        \item {Performed specialized and monetary account maintenance, reviewed credit reports to determine elgibility, processed applications for accounts including Trust, Power of Attorneys, and Individual Retirement Accounts.}
        \item {Collaborated as a multidisciplinary team to solve complex account issues, ensuring all activities complied with internal policies and regulatory guidelines.}
        \item {Served as a mentor to teammates by providing expertise on products, systems, and operational processes.}
         	\end{cvitems}
    } 

  \cventry
    {Member Service Representative} % Job title
    {} % Organization
    {} % Location
    {November 2015 - November 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Presented and recommended Credit Union products and services to members to assist in meeting individual financial needs.}
        \item {Researched and resolved account inquiries to ensure the highest quality member service.}
        \item {Assisted members with submitting applications for membership, deposit accounts, consumer loans, credit cards, personal and overdraft lines of credit.}
         	\end{cvitems}
    } 
    
    \cventry
    {Direct Support Professional} % Job title
    {Dungarvin} % Organization
    {Eugene, OR} % Location
    {November 2013 - November 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Supported individuals with developmental disabilities in areas of behavior management, life skills, healthcare, and community integration. }
      \end{cvitems}
    }     
    
    \cventry
    {Customer Sales and Service Representative} % Job title
    {GSI Commerce/Radial, Inc.} % Organization
    {Eau Claire, WI} % Location
    {August 2010 - July 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Answered customer calls and emails for e-commerce business, met and exceeded sales quotas and service objectives in a fast-paced call center environment.}
      \end{cvitems}
    }   
     
    \cventry
    {Copy Chief}
    {The University of Wisconsin-Press}
    {Madison, WI}
    {May 2008 - May 2010}
    {\begin{cvitems}
      \item{Wrote and edited marketing copy, negotiated input from authors and editorial and marketing departments to develop and finalize copy.}
    \end{cvitems}
    }


\end{cventries}

